---
title: "DWDM Project Analysis"
output: html_notebook
---
<h4>
Members:<br>
<ol>
<li><strong>Kaivan Shah</strong></li>
<li><strong>Navneet Kishan</strong></li>
</ol>

This is an R notebook containing the analysis of the Job Postings from naukri.com<br>
Data has been obtained from web scraping and analyzed here.<br>
Presently contains basic Exploratory analysis techniques and further analysis and models to be built eventually.<br>
<br>
<strong>OBJECTIVE:</strong> To analyze various trends in jobs for a particular period of time and make a simple linear model to predict Lowest Salary for a job based on the experience level.
</h4>

```{r}
#install.packages('Amelia')
#install.packages("ggplot2")
#install.packages("tidyr")
library(Amelia)
library(magrittr)

df<-read.csv("./refined_data.csv", header = TRUE)
#print(df)

missmap(df)
#after refining
```
Shows the Missing Attributes for a certain row value.

```{r}
ggplot(data = df, aes(x=org, y=salLow))+geom_bar(stat = "identity")
```


```{r}
matr<-data.matrix(df, rownames.force = NA)
#print(matr)
corr<-cor(matr)
#matr<-matrix(df$expLow, nrow = 25, ncol = 25)
print(corr)
heatmap(as.matrix(corr), scale = "column",Rowv = NA, Colv = NA)

```

```{r}
matr<-data.matrix(df, rownames.force = NA)
#print(matr)
#corr<-cor(matr)
#matr<-matrix(df$expLow, nrow = 25, ncol = 25)
matr2<-matrix(c(df$expLow, df$salLow), nrow = 100, ncol = 100)
corr<-cor(matr2)
#print(corr)
heatmap(as.matrix(corr), scale = "column",Rowv = NA, Colv = NA)

```

k means here:
```{r}
#location wise lowest salary
ggplot(data = df, aes(x=loc, y=salLow))+geom_bar(stat = "identity")+ theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
```{r}
#total non null attributes and the count of those values
c<-sapply(df, function(x) length(unique(x)))
c
```

```{r}
#values of each attribute
lab<-c('designation','details','org','loc','keyskills','date','salLow','salHigh')
color<-c("#344AF7", "#4875F5", "#65A6F7","#85E0F7", "#89E5F7")
pie(c(622,622,459,174,727,94,34,38), labels = lab, col = color)
```

```{r}
ggscatter(df, x="expLow", y="salLow", add = "reg.line", cor.coef = TRUE, conf.int = TRUE, cor.method = "pearson")
#as p > 0.05, hence correlation not statistically significant
```

```{r}
ggscatter(df, x="expHigh", y="salHigh.", add = "reg.line", cor.coef = TRUE, conf.int = TRUE, cor.method = "pearson")
#as p<0.05, hence correlation statistially significant, with a correlation #coefficient of 0.11 which is a weak but positive relation.
```

```{r}
#Linear model

#lmMod <- lm(dist ~ speed, data=trainingData)  # build the model
#distPred <- predict(lmMod, testData)

testData<-read.csv("./naukriWebDeveloper_01.csv")
mod<-lm(formula = salHigh. ~ (expHigh - expLow), data = df)
mod
distPred <- predict(mod, df)
distPred
as.data.frame(distPred)

```
Predicted values in a new Data Set
<hr></hr>
```{r}
library(lubridate)

#extracting only month
om<-month(as.POSIXlt(df$date, format="%d-%m-%Y"))
#om
omm<-as.data.frame(om)
omm
tm<-sapply(omm, function(x) (unique(x)))
tm

#getCount function
getCount <- function(x) {
  u <- unique(x);
  data.frame(
     value=u,
     count=sapply(u, function(v) { length(which(x==v)) } )
  )
}

cnt<-getCount(om)
plo<-as.data.frame(cnt)
plo

pie(c(plo$count), labels = c("Feb", "Mar", "Apr"), col = color)

```

```{r}
om<-month(as.POSIXlt(df$date, format="%d-%m-%Y"))

df2<-cbind(df,om)
#Extracting opportunities only in MARCH
fil<-subset(df2,om==3, select = (desig))
fil<-as.data.frame(fil)

#making all attributes uniform to compare easily for analysis

#all to upper case
df3<-toupper(fil$desig)
#library(plan)
head(df3)

#Remove Whitespaces
df4<-sapply(df3,function(x) gsub(" ","",x))
as.data.frame(df4)

#All Designations made uniform
df5<-getCount(df4)
as.data.frame(df5)
```
```{r}
#extracting job opportunities > 1
df6<-subset(df5, count>1, select = c(value, count))
df6

ggplot(data=df6, aes(x=value, y=count))+geom_bar(stat="identity", fill="#FF6666")+theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
```{r}
library(cluster)
library(fpc)

as.data.frame(distPred)
dat<- df$expLow
clus <- kmeans(dat, centers = 3)
clus
df

```

```{r}
plotcluster(dat, clus$cluster)

```

```{r}
#finding salary along with the job as a factor in linear model

nd<-read.csv("./new_data.csv")
nd
mod<-lm(formula = salLow ~ (expHigh - expLow + job), data = nd)
#mod
distPred <- predict(mod, nd)
#distPred
as.data.frame(distPred)

test<-read.csv("./new_test.csv")
res<-predict(mod, test)
res1 = as.data.frame(res)
head(res1)
cbind(test, res1)

```

```{r}
```

